### 2009-05-20 doc/tech_doc/infosys/infosys_technical.tex
Few words about design/architecture of infosys

@@

 In case of multiple ISIS services they form a peer-to-peer network. Inside that cloud Registration Records are propagated between services in such a way that all ISIS instances continiously try to synchronise their databases.

@@

  \item[Output]~\begin{description}
    \item[Fault] Optional element describing fault which occured while performing registration. If missing registration succeeded.
  \end{description}

@@

Service must supply mandatory information. Among those the \texttt{Endpoint Reference} is used to contact service - only required element is contact URL of service. \texttt{Type} specifies kind of service and is used to find out functionality nad interface of service. \texttt{ServiceID} is used to distinguish between registered services and to deal with case of service changing it's contact URL. For more information about mandatory and optional information see Section \ref{service_advertisement}

@@

This operation is used to explicitely requesting the removal of zero or more Registration Entries associated with specified ServiceID values stored in the Information System. If corresponding record does not exist it's identifier will be present in response message together with corresponding Fault element.

@@

\subsection{Client Authorzation}
\label{sub:isis_authorization_client_authorization}

@@

To ensure information stored in ISIS cloud can't be tampered and only available to proper clients following authorization framework is implemented. All actions perfored by ISIS clients are divided into three following groups:

@@

 Those operations may cause uncontrollable changes in colleccted information and must be granted only for higly trusted entities like ISISes themselves.

@@

Those 3 action groups are handled using Security Framework of ARC~\cite{arcsec}. For each group corresponding 
Action is defined for ARC policy language as descriped in table \ref{tab:policy_actions}.

@@

\subsection{Information Authorzation}
\label{sub:isis_authorization_information_authorization}

@@

To implement functionality described above each node in agregated XML documents of information
collected by ISIS cloud may have Access Control Policy associated with it. Access control is 
defined at level of XML node and propagates all children nodes - similar to file systems.
Children nodes can only additionally restrict access control imposed by parent node. For example
if parent node A allows access only to VO1 then children node B can narrow access to Adminsitrator 
of VO1 and can't grant access for VO2 members.

By default all XML nodes are public. Access Control Policies are embedded into XML document
as XML nodes (see Appendix \ref{annex:info_policies_schema} for schema) even if that violates schema 
of document. Then nodes are assigned policies aby adding XML attributes refering to defined Policies.
Access permission to particular information node is evaluated by traversing all nodes prom 
parent to childen. At first node which gives negative result evaluation is stopped and
this node including all its children is removed from document.

@@

Every service registering to ISIS should also provide an interface for direct querying of information 
describing service. Normally this information should be more detailed than one sent to ISIS. For this 
purpose LIDI interface is defined which is a susbset of WS Resource Properties (WSRP)~\cite{wsrf-rp}. Following WSRP
operations must be supported - \textit{GetResourcePropertDocument}, \textit{GetResourceProperty},
\textit{GetMultipleResourceProperties} and \textit{QueryResourceProperties}.

@@

To register services to more than one ISIS network multiple Registrant instances has to be configured. In this case, the default Registrant will be used for registering every services unless configured expilicitely.
The registration of service can be done once or periodically based either on the configuration of the Registrant or overwritten for every service separately. The Registrant is also performing message aggregation of all services linked to it if possible. The simplified algorithm of the Registrant is presented below.

@@

Registration parameters per service are defined by InfoRegister element located inside corresponding service configuration element. To assign service to specific Registrant(s) ona may use Registrar configuration elements situated inside InfoRegister. If none Registrar element is defined service will be registed using first (default) Registrant. To make not register itself special configration element NoRegister has to be used.

Following elements are defined inside configuration element if the Registrant:
\begin{description}
\item{URL}            <!-- URL specifies contact endpoint of a bootstrap Information
                 Registration service. Further ISIS adresses will be queried
                 from this service. -->
\item{KeyPath, CertificatePath, ProxyPath and CACertificatesDir}
            <!-- Optional KeyPath, CertificatePath, ProxyPath and CACertificatesDir are
                 paths to files storing X509 credentials used for establishing connections. -->
\item{Retry}            <!-- Retry count. Specifie how many times have an ISIS to timeout to handle it as
                 unavailable. If there is no value specified the default value: 5 will be used. -->
            <xsd:element name="Retry" type="xsd:string" minOccurs="0" maxOccurs="1"/>

>>>>

\begin{figure}[ht]
\centering{{\scalebox{0.6}{\includegraphics{InfosysArchitecture.png}}}
\caption{\label{fig:infosys_architecture}Architecture of Information System} }
\end{figure}

Information System of ARC middleware is composed of 3 main parts. The Information System Indexing Services (ISIS) for a set of information containers. Every generic ARC Service pushes information about itself into nearby ISIS container/service hence registering itself to Information System. The information stored in every ISIS is propagated among all ISIS services. Clients can query any nearby ISIS service for registered information in order to perform discovery of services which posses specific properties.

@@

 In case of multiple ISIS services they form a peer-to-peer network. Inside that cloud Registration Records are propagated between services in such a way that all ISIS instances continuously try to synchronize their databases.

@@

  \item[Output]~\begin{description}
    \item[Fault] Optional element describing fault which occurred while performing registration. If missing registration succeeded.
  \end{description}

@@

Service must supply mandatory information. Among those the \texttt{Endpoint Reference} is used to contact service - only required element is contact URL of service. \texttt{Type} specifies kind of service and is used to find out functionality and interface of service. \texttt{ServiceID} is used to distinguish between registered services and to deal with case of service changing it's contact URL. For more information about mandatory and optional information see Section \ref{service_advertisement}

@@

This operation is used to explicitly requesting the removal of zero or more Registration Entries associated with specified ServiceID values stored in the Information System. If corresponding record does not exist it's identifier will be present in response message together with corresponding Fault element.

@@

\subsection{Client Authorization}
\label{sub:isis_authorization_client_authorization}

@@

To ensure information stored in ISIS cloud can't be tampered and only available to proper clients following authorization framework is implemented. All actions performed by ISIS clients are divided into three following groups:

@@

 Those operations may cause uncontrollable changes in collected information and must be granted only for highly trusted entities like ISISes themselves.

@@

Those 3 action groups are handled using Security Framework of ARC~\cite{arcsec}. For each group corresponding 
Action is defined for ARC policy language as described in table \ref{tab:policy_actions}.

@@

\subsection{Information Authorization}
\label{sub:isis_authorization_information_authorization}

@@

To implement functionality described above each node in aggregated XML documents of information
collected by ISIS cloud may have Access Control Policy associated with it. Access control is 
defined at level of XML node and propagates all children nodes - similar to file systems.
Children nodes can only additionally restrict access control imposed by parent node. For example
if parent node A allows access only to VO1 then children node B can narrow access to Administrator 
of VO1 and can't grant access for VO2 members.

By default all XML nodes are public. Access Control Policies are embedded into XML document
as XML nodes (see Appendix \ref{annex:info_policies_schema} for schema) even if that violates schema 
of document. Then nodes are assigned policies by adding XML attributes referring to defined Policies.
Access permission to particular information node is evaluated by traversing all nodes prom 
parent to children. At first node which gives negative result evaluation is stopped and
this node including all its children is removed from document.

@@

Every service registering to ISIS should also provide an interface for direct querying of information 
describing service. Normally this information should be more detailed than one sent to ISIS. For this 
purpose LIDI interface is defined which is a subset of WS Resource Properties (WSRP)~\cite{wsrf-rp}. Following WSRP
operations must be supported - \textit{GetResourcePropertDocument}, \textit{GetResourceProperty},
\textit{GetMultipleResourceProperties} and \textit{QueryResourceProperties}.

@@

To register services to more than one ISIS network multiple Registrant instances has to be configured. In this case, the default Registrant will be used for registering every services unless configured explicitly.
The registration of service can be done once or periodically based either on the configuration of the Registrant or overwritten for every service separately. The Registrant is also performing message aggregation of all services linked to it if possible. The simplified algorithm of the Registrant is presented below.

@@

Registration parameters per service are defined by InfoRegister element located inside corresponding service configuration element. To assign service to specific Registrant(s) one may use Registrar configuration elements situated inside InfoRegister. If none Registrar element is defined service will be registered using first (default) Registrant. To make not register itself special configuration element NoRegister has to be used.

Following elements are defined inside configuration element if the Registrant:
\begin{description}
\item{URL}            <!-- URL specifies contact endpoint of a bootstrap Information
                 Registration service. Further ISIS addresses will be queried
                 from this service. -->
\item{KeyPath, CertificatePath, ProxyPath and CACertificatesDir}
            <!-- Optional KeyPath, CertificatePath, ProxyPath and CACertificatesDir are
                 paths to files storing X509 credentials used for establishing connections. -->
\item{Retry}            <!-- Retry count. Specifies how many times have an ISIS to timeout to handle it as
                 unavailable. If there is no value specified the default value: 5 will be used. -->
            <xsd:element name="Retry" type="xsd:string" minOccurs="0" maxOccurs="1"/>
